The Sam Mark I has been developed to solve one of aviation's biggest challenges: congested airports in urban areas prone to significant delays.  As airlines continue to embrace the hub and spoke model, it becomes ever apparent modern aviation has ignored one of the biggest necessities in the market - a high capacity plane optimized to handle shorter routes while still retaining the capability of long-haul nonstop flight between the world's major destinations. A twin engine wide body, the Sam Mark I will be capable of comfortably carrying 400 passengers in a 50/350 2-class configuration with adequate range to fly transatlantic from the Eastern seaboard to European destinations.  Unlike many competitors, the Sam Mark I takes full advantage of contemporary composites and high-lift devices in order to feature a fully composite wing adjacent to traditional fuselage, resulting in a significant increase in performance and added value to the end user.  This value will only increase as populous economies across the world mature, resulting in an increased demand on commercial aviation that not only fits within but also fully utilizes the existing infrastructure. 
\textcolor{red}{
\begin{itemize}
    \item Discuss motivation, design objectives (e.g design drivers, key requirements), and a summary of key design characteristics and capabilities. 
    \item This section should identify your niche (i.e. who your target customers are), convince the reader to read the rest of the report, and provide context for the remaining discussion. 
    \item Discuss any unique attributes to your design philosophy. 
    \item Start pagination as: 1, 2, 3,... \checkmark
\end{itemize}}